\tool: Revisiting BadUSB with Type-C

### 2021-03-19 WOOT/BadUSBC.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

The security of the \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused severe problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
    multi-mode attack model, \tool.  This obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments and a user study on a real-life attack
    scenario.  Ten volunteers participated. 4,172 of 94,058 records
    obtained by \tool in the user study are related to sensitive information.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

>>>>

The security of the \ac{USB} protocol has been paid extensive attention to because of its
    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
    security has caused severe problems.  For example, a well-known firmware
    attack, BadUSB, performs malicious operations on the victim hosts through
    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
    multi-mode attack model, \tool.  This obtains UI status to make attacks more 
    precise and effective.  To the best of our knowledge, \tool is the first attack model
    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
    conducted extensive experiments to simulate daily usage and summarized the private information collected.
%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
    %isolated UI rendering.}
We also discussed the recommended countermeasures for our attack model,
    including isolated UI rendering, which may be inspiring for future research
    on defense methods.
\end{abstract}

### 2021-03-19 WOOT/Files/conclusion.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The fully control mode
achieves the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

\section{Responsible Disclosure}
Responsible disclosure have already been carried out, we have already contacted HUAWEI and Apple through proper channel. We received response from HUAWEI on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet. HUAWEI security team has confirmed this issue and been weighing different mitigation approaches. We are actively facilitating their mitigating process and waiting for mitigation to be deployed.

>>>>

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB. The video capture mode proved practical and powerful, as it extracts
victim's sensitive information in a stealthy way. The fully control mode
achieves the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

\section{Responsible Disclosure}
Responsible disclosure have already been carried out, we have already contacted HUAWEI and Apple through proper channel. We received response from HUAWEI on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet. HUAWEI security team has confirmed this issue and been weighing different mitigation approaches. We are actively facilitating their mitigating process and waiting for mitigation to be deployed. After the mitigation is deployed, HUAWEI will apply a CVE ID for this vulnerability.

### 2021-03-19 WOOT/Files/experiment.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

We notice that, with \tool, the attacker can view any victim's information that does not require authentication with video capture mode or full control mode.
However, the information that requires authentication can only be obtained with video capture mode after the victim's authentication.
To further validate our attacking scenario, we conduct an experiment to find out what types of sensitive information are protected by default. We selected 11 applications on Android, set up each application with the strategy that
\yechang{Application version....????}
\ding{182} Login in with a test account,
\ding{183} Keep the default settings,
\ding{184} Agree to it when it asks to enable authentication before accessing private data,
then recorded all information shown in applications with or without authentication.
It is worth mentioning that {secure keyboards} built-in financial apps show their keyboard typing sequences, which can be easily captured by \tool.

As the result shown in Table~\ref{table:information_extracted}, most payment applications use in-app authentication to ensure payment security but biometric authentication is not enabled by default. If the victim uses a password instead of biometric authentication, the password can be leaked out and used to guess screen unlock passcode or hack accounts, which threats the victim's property.
And the leakage of the information that can be obtained without authentication is sufficient to bring potential risk to the victim, such as misappropriating the victim's payment code, using the victim's personal information for illegal crimes.

In summary, if the user unconsciously unlocks the screen and visits corresponding applications, we can still view all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal property status.
The information that requires authentication is safer than the information that does not require authentication. The attacker can not directly obtain this kind of information aggressively through the full control mode. But the possibility of the leakage of information that needs authentication would increase as the victim uses the device.

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\multirow{2}{*}{\textbf{Category} } & \multirow{2}{*}{ \textbf{Application} } & \multicolumn{2}{c|}{\textbf{Leaked Sensitive Information}} \\
															\cline{3-4}
											&				& \textbf{Without Authentication}						& \textbf{With Authentication} \\
		\hline
		Social \& Finance App 				& WeChat      & Account, Property Status, Chat History, Payment Code   		& Payment Password \\
		\hline
		\multirow{3}{*}{Social App}
											%& QQ          & Account, Interpersonal Nexus, Chat History   	& \\
											%\cline{2-4}
							       			& WhatsApp    & Account, Interpersonal Nexus, Chat History, Phone Number    & \\
											\cline{2-4}
							       			& Facebook    & Account, Posts, Interpersonal Nexus, Contact Info           & \\
		\hline
		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Property Status, Payment Code         				& Payment Password \\
											\cline{2-4}
											& Cash App    & Email, Phone Number, Cash Balance							& Payment Password \\
											\cline{2-4}
											& Paypal      & Account, PayPal Balance     								& Payment Password \\
		\hline
		\multirow{1}{*}{Shopping App}		& Amazon Shopping  & Account, Orders, Shopping Cart         				& \\
											%\cline{2-4}
		                					%& Taobao      & Personal physical metrics      						& \\
		\hline
		\multirow{2}{*}{Tool}               & Chrome      & Browsing History                                	& \\
											\cline{2-4}
		                					& Health      & Personal Physical Metrics      						& \\
		\hline
		\multirow{2}{*}{System}             &  Messages   & Interpersonal Nexus, Chat History, Contacts' Phone Number &   \\
											\cline{2-4}
											& Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
											\cline{2-4}
		                					& Settings - VPN    & VPN address, VPN account, VPN password      						& \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Sensitive Information Leaked From Applications.}
	\label{table:information_extracted}
\end{table*}

>>>>

To further validate our attacking scenario, we conducted an experiment to simulate a real-world attack scenario. We selected 11 applications on  \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
\ding{182} Attach \tool to the test device.
\ding{183} Login in with a test account.
\ding{184} Keep the default settings.
\ding{185} Simulate daily usage of the application.

During this experiment, we first tested full control mode which actively gathered sensitive information, then tested video capture mode which passively collected the sensitive information visited by victims. We noticed that, most sensitive information could be gathered directly through full control mode without victim's interaction, but there was also certain information that had to be collected passively through video capture mode. For example, as illustrated in Table~\ref{table:information_extracted}, in most applications, information like `Account' can be gathered directly while information like `Payment Password' cannot be collected until the victim inputs his/her password.

\subsubsection{Result}
In summary, as shown in Table~\ref{table:information_extracted}, our \tool is able to actively gather most sensitive information such as browsing history, personal account, phone number without victim's interaction. There also exists information such as payment password that is not available immediately, but such a piece of information can be collected once the victim input it on his/her smartphone. The gathered information can be further used to deduce victim's lock screen password and poses even greater threat to victim's privacy.

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|l|l|c|c|}
		\hline
		\multirow{2}{*}{\textbf{Category} } & \multirow{2}{*}{ \textbf{Application} } & \multicolumn{2}{c|}{\textbf{Leaked Sensitive Information}} \\
															\cline{3-4}
											&				& \textbf{Without Authentication}						& \textbf{With Authentication} \\
		\hline
		Social \& Finance App 				& WeChat      & Account, Property Status, Chat History, Payment Code   		& Payment Password \\
		\hline
		\multirow{3}{*}{Social App}
											%& QQ          & Account, Interpersonal Nexus, Chat History   	& \\
											%\cline{2-4}
							       			& WhatsApp    & Account, Interpersonal Nexus, Chat History, Phone Number    & \\
											\cline{2-4}
							       			& Facebook    & Account, Posts, Interpersonal Nexus, Contact Info           & \\
		\hline
		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Property Status, Payment Code         				& Payment Password \\
											\cline{2-4}
											& Cash App    & Email, Phone Number, Cash Balance							& Payment Password \\
											\cline{2-4}
											& Paypal      & Account, PayPal Balance     								& Payment Password \\
		\hline
		\multirow{1}{*}{Shopping App}		& Amazon Shopping  & Account, Orders, Shopping Cart         				& \\
											%\cline{2-4}
		                					%& Taobao      & Personal physical metrics      						& \\
		\hline
		\multirow{2}{*}{Tool}               & Chrome      & Browsing History                                	& \\
											\cline{2-4}
		                					& Health      & Personal Health Metrics      						& \\
		\hline
		\multirow{2}{*}{System}             &  Messages   & Interpersonal Nexus, Chat History, Contacts' Phone Number &   \\
											\cline{2-4}
											& Settings - WiFi   & WiFi SSID                                	&  WiFi Password \\
											\cline{2-4}
		                					& Settings - VPN    & VPN Address, VPN Account, VPN Password      						& \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Sensitive Information Leaked From Applications.}
	\label{table:information_extracted}
\end{table*}

### 2021-03-19 WOOT/Files/related_work.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
JFA~\cite{JFC}, short for Juice Filming Attacks,
abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although JFA~\cite{JFC} could  exfiltrates video data from the victim without permission,  
there are two main limitation compared with \tool: 
\ding{183} JFA~\cite{JFC} can only exfiltrate video data under from victim's device, while \tool can control the victim's device at the same time as monitoring the screen. For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device. However \tool can open the payment application by mouse, exfiltrate the payment QR code, and steal money by scanning the payment QR code.
\ding{182} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} are released in 2015, a lack of support of \ac{MHL} limits the capabilities of JFA. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB blocks its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
an alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious devices in the user's absence until the session is unlocked.

>>>>

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
JFA~\cite{JFC}, short for Juice Filming Attacks,
abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitation compared with \tool: 
\ding{182} JFA~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection. For example, if the victim leaves his/her phone charging without locking it, the JFA cannot obtain anything in this case, while \tool can actively control victim's device and gather sensitive information.
\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB blocks its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from USB Request Blocks, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
an alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious devices in the user's absence until the session is unlocked.
